### 2016-12-05 methodsPaper/tex/materialsAndMethods.tex

As with the original ITHIM implementation we, employed a comparative
risk assessment (CRA) across scenarios defined by mean active
transportation time, i.e., combined walking and cycling.  To do so we
investigate the proportional change in national disease burden between
the baseline model and a given alternative scenario, i.e., the
population attributable fraction, $\af$.  The population attributable
fraction is defined below and computed for each disease (ICD-10) included in
the model, namely Breast Cancer (C50), Colon Cancer (C18-C21), Depression (??), Dementia (G30),
Diabetes (E10-E14) and Cardiovascular disease (I10, I12, I15, I20-I25, I30-I31, I33, I40).  For readability we omit an index
indicating disease.

>>>>

As with the original ITHIM implementation we, employed a comparative
risk assessment (CRA) across scenarios defined by mean active
transportation time, i.e., combined walking and cycling.  To do so we
investigate the proportional change in national disease burden between
the baseline model and a given alternative scenario, i.e., the
population attributable fraction, $\af$.  The population attributable
fraction is defined below and computed for each disease (ICD-10) included in
the model, namely Breast Cancer (C50), Colon Cancer (C18-C21), Dementia (G30),
Diabetes (E10-E14) and Cardiovascular disease (I10, I12, I15, I20-I25, I30-I31, I33, I40).  We also include the disability impacts of depression, though it is not listed as a cause of death in CDC's data. For readability we omit an index
indicating disease.

### 2016-12-05 methodsPaper/tex/results.tex

We report total change (averted or increased) in diability adjusted
life years (DALYs) as an estimate of dissease burden change with
alternative scenarios.

To estimate DALYs we use a methodology adopted from previous US
implementations of ITHIM which scale Global Budern of Disease
Estimates for the US to smaller populations using mortality rate
ratios \cite{maizlish2013}. Age, sex, and casuse specific mortalities
were obtained form the CDC WONDER database for US metro counties for
the years 2010-2014. Cells with less than 10 deaths were imputed using
R's random integer generator.

Our subset of the US population to only metropolitan counties
consisted of 1,090 of 3,141 (34.7\%) counties, or ???X??? of ???Y???
(???Z???\%) of the total US population. The age and gender
distribution of our subset population was slightly younger (???making
this up???) than the national population. Active transport times
(walking and cycling) for baseline, low, and high scenarios are shown
in \ref{fig2}. Overall mean walking time for high and low
scenarios were ???X??? (min/week) higher and ???Y??? (min/week) lower
than baseline, respectively. Baseline non-travel activity time was
estimated to be ???X??? (min/week) from the ATUS for US metropolitan
populations.

Comparing baseline to low/high scenarios produced estimates of ???X???
change in the disease burden (1,000s DALYs) for our US population
subset. We then varied the mean non-travel activity time and active
travel time to observe how this chaged results (\ref{fig1}). We
observe the most dramatic responses in disease burden estimates to
changes in active travel time when non-travel activity times are
lowest. This result is consistent with the non-linear dose-response
curve for physical activity and several health outcomes. The total
health benefit of increased active travel time (high scenario) varies
from ???X??? to ???Y??? with changing mean non-travel activity time (0
to 25 minutes).

@@

As exhibited in Figure \ref{fig1}, the variability in disease burden
benfits varies to a much greater degree when using fewer points in the
attirbutable fraction approximation.

>>>>

We report total change (averted or increased) in diability adjusted
life years (DALYs) as an estimate of disease burden change with
alternative scenarios.

To estimate DALYs we use a methodology adopted from previous US
implementations of ITHIM which scale Global Budern of Disease
Estimates for the US to smaller populations using mortality rate
ratios \cite{maizlish2013}. Age, sex, and casuse specific mortalities
were obtained form the CDC WONDER database for US metro counties for
the years 2010-2014. Cells with mortality counts less than 10 deaths were suppressed for privacy and imputed (0 to 9) using
R's random integer generator.

Our subset of the US population to only metropolitan counties
consisted of 1,090 of 3,141 (34.7\%) counties, or approximately 272M of 312M
(87\%) of the total US population. The age and gender
distribution of our subset population was slightly younger (???making
this up???) than the national population. Baseline active transport times
(walking and cycling) for the US across age and sex groupings was found to be approximately 43 min/week (???). Baseline non-travel activity time was found to be ???X??? (min/week) from the ATUS for US metropolitan
populations.

@@

As exhibited in Figure \ref{fig1}, the variability in disease burden
benefits varies to a much greater degree when using fewer points in the
attirbutable fraction approximation. Importantly, we see greater stability when using
the package and percentiles to approximate attirbutable fraction.

Comparing baseline to scenarios with increased active travel produced estimates of up to
360,000??? fewer DALYs (with 300\% increase in mean active travel time) for our US population subset. We then varied the mean non-travel activity time and active
travel time to observe how this chaged results (\ref{fig1}). We
observe the most dramatic responses in disease burden estimates to
changes in active travel time when non-travel activity times are
lowest. This result is consistent with the non-linear dose-response
curve for physical activity and several health outcomes.
